Project Proposal: Implementing Flow-based Balanced Bipartition Algorithm

### 2014-04-25 sequential/latex/abstraction/iwls/intro_iwls.tex
upload files from laptop linux

Abstraction of word-level functionality from bit-level descriptions of
digital circuits is an important fundamental problem in Electronic
Design Automation (EDA) and design verification. Word-level abstractions
find applications in high-level/RTL datapath synthesis
\cite{demicheli:iccad_98} \cite{demicheli:dac_99}
\cite{demicheli:tcad_03}, RTL verification \cite{WLS} \cite{arditi:bmd}
\cite{lpsat}, word-level SMT and constraint solving \cite{ms:research}
\cite{boolector} \cite{tew:iccad08}, and can also be
applied to detect malicious modifications to a circuit -- potentially
inserted as hardware Trojan horses -- by reverse-engineering the
function implemented by the circuit. It is further desirable that the
obtained word-level abstraction be a {\it canonical} representation of
the function, to facilitate equivalence verification between a
specification model and an implementation circuit. This master's
thesis proposes the investigation of the problem of deriving word-level,
canonical, polynomial representations from circuits over Galois fields
using concepts from commutative algebra and algebraic geometry ---
notably, Gr\"obner bases \cite{gb_book}, Buchberger's algorithm
\cite{buchberger_thesis}, elimination ideals \cite{ideals:book}, 
and the FGLM algorithm \cite{fglm}.

The main motivation for this work is to ``reverse engineer'' or
identify the function implemented by a given Galois field arithmetic 
circuit as used in Elliptic Curve Cryptography (ECC). The main
operations of encryption, decryption and authentication in ECC rely on
point-addition and point-doubling operations on elliptic curves
defined over Galois fields $\Fkk$. These primitive operations are, in
turn, implemented as circuits that perform polynomial computations
over $k$-bit vectors \cite{eccld}. 
%Moreover, the datapath size $k$ in these applications
%can be very large, {\it e.g.} $k = 163, 233$ and larger, as specified
%by the US National Institute for Standards and Technology (NIST) for
%ECC. 
The objective is to apply our approach to a given circuit and
{\it extract  the word-level polynomial function} implemented by
it for design verification. The mathematical problems addressed in
this proposal, and the approaches to solve them, are described below:

{\bf Problem Statement:} Given a combinational circuit $C$ with
$k$-bit inputs and $k$-bit outputs, such that the circuit implements 
Boolean functions that are mappings between $k$-dimensional Boolean
spaces: $f: \B^k \rightarrow \B^k$. Let $\{a_0, \dots, a_{k-1}\}$
denote the primary inputs of the circuit, and let $\{y_0, \dots,
y_{k-1}\}$ denote the bit-level primary outputs. Suppose that we do
not know the function implemented by the circuit. We wish to
derive a {\it word-level, symbolic representation} of the function as
$Y = \F(A)$, where $Y = \{y_0, \dots, y_{k-1}\}$, $A = \{a_0, \dots, 
a_{k-1}\}$ are, respectively, the output and input bit-vectors,
and $\F$ denotes a polynomial representation of the
function $f$. We wish to further generalize our approach to any
circuit with arbitrary number  of inputs ($n$) and outputs ($m$), as
polynomial functions $f: {\mathbb{F}}_{2^n} \rightarrow
{\mathbb{F}}_{2^m}$.

{\bf Approach:} At a Boolean-level, canonical symbolic DAG
representations of functions have been extensively investigated; such
as decisions diagrams (ROBDDs \cite{BRYA86}, FDDs \cite{okfdd}),
moment diagrams (BMDs \cite{bmd}, K*BMDs \cite{kbmd}) and their
word-level variants \cite{WLS}. However, the decomposition principle
behind these representations is based on (variants of) the Shannon's
expansion, which is a bit-wise, Boolean decomposition. Such
approaches cannot be efficiently applied to word-level abstraction of
modulo-arithmetic circuits over Galois extension fields
$\Fkk$. Therefore, we approach this problem from a symbolic commutative
algebra perspective.

@@

First of all, {\it not every
  function} of the type $f: \Z_{2^k} \rightarrow \Z_{2^k}$, is a
polynomial function; i.e. every function cannot be represented by a
polynomial $\F \pmod{ 2^k}$.  In commutative algebra, identification of
such polynomial functions is an important problem: i.e.  given a function
$f: \Z_n \rightarrow \Z_n$, $n \in {\mathbb{N}}$, identify if $f$ has
a polynomial representation. If so, derive a unique,
minimal, canonical polynomial $\F$, such that $f \equiv  \F \pmod{
  n}$. 
%that represents $f$. 
%This
%requires to analyze $f$ at each of the $n$ points, and to setup a
%system of $n$ linear congruences to solve. If this system of
%congruences has a solution, then $f$ is a polynomial function; 
%otherwise, $f$ is not a polynomial function. And the feasible
%solutions to these linear congruences correspond to the coefficients
%of a polynomial $\F$ that represents $f$.  
The papers
\cite{singmaster} \cite{chen_95} \cite{chen_96} addressed such
problems in number theory and algebra. {\it
 Shekhar} \cite{shekhar:phd} also addressed RTL verification of
polynomial datapaths over $k$-bit vectors using the above
concepts. However, in her work, the RTL datapath was already known to
be a polynomial function $\pmod{ 2^k}$. Unfortunately, an arbitrary
$k$-input/$k$-output combinational circuit cannot always be modeled as
a polynomial function over $\Z_{2^k}$; therefore, the $\Z_{2^k}$ model
is not considered in this work.

On the other hand, there is a well-known ``textbook'' result
\cite{ff:1997} which states that over Galois fields ($\Fq$) of $q$
elements, {\it every function} $f: \Fq \rightarrow \Fq$ is a
polynomial function. 
%By analyzing $f$ over each of the $q$ points, one can apply
%Langrange's interpolation formula and interpolate a polynomial $\F(x)
%= \sum_{k=1} ^q  \frac{ \prod_{i \neq k}  (x -x_i)}{\prod_{i \neq k}
%  (x_k -x_i)} \cdot f(x_k)$, which is a polynomial of degree at 
%most $q-1$ in $x$. One can easily see that $\F(a)=f(a)$ for all $a \in
%\Fq$, and $\F(x)$ is therefore the polynomial function representation
%of $f$. 
Motivated by this fundamental result, we will devise an approach
to extract a word-level polynomial function (abstraction) from a
circuit. Given the circuit $C$ which represents a function $f:
\B^k \rightarrow \B^k$, we will interpret $f$ as a function $f: \Fkk
\rightarrow \Fkk$, and derive a unique, minimal, canonical polynomial
representation as $Y = \F(A)$ over $\Fkk$, where $Y, A$ are,
respectively, the output and input bit-vectors of the circuit
$C$. 
%Note, however, that we are not given a function (mapping);
%rather, we are given a circuit, which is an encoding of the
%function. Interpolating a polynomial $\F$ over $2^k$ points is
%also going to be infeasible for large values of $k$. Therefore, 
We will extract a set of polynomials (ideal) from the circuit and employ
{\it Gr\"obner bases} techniques to abstract the canonical polynomial
representation. Our approach can be generalized to a circuit with
arbitrary number of inputs and outputs, i.e. to analyze polynomial
functions $f: \Fq^d \rightarrow \Fq$, $q = 2^k$, and further to $f:
{\mathbb{F}}_{2^n} \rightarrow {\mathbb{F}}_{2^m}$.

\begin{Example}
{\bf Motivating Example:} {\it
Consider a 2-bit multiplier circuit over ${\mathbb{F}}_{2^2}$ given in
Fig. \ref{fig:mul2bit}, which implements a function $f: {\mathbb{F}}_4
\times {\mathbb{F}}_4 \rightarrow {\mathbb{F}}_4$. It implements a
{\bf polynomial function}: $Z = A \times B, ~Z, A, B \in
{\mathbb{F}}_4$. Variables $a_0, a_1, b_0, b_1$ are primary inputs,
$z_0, z_1$ are primary outputs, and $s_0, s_1, s_2, s_3, r_0$ are
intermediate variables of the circuit. 
These bit-level variables are in ${\mathbb{F}}_2 = \{0, 1\}$.
%variables $a_0, a_1, b_0, b_1, g_0, g_1, s_0, s_1, s_2, s_3, r_0$ are
%in ${\mathbb{F}}_{2}$. 
Then, we can consider $A = a_0 + a_1 \alpha, ~B = b_0 +
b_1 \alpha$ as the word-level inputs and $Z = z_0 + z_1 \alpha$ 
as the output in ${\mathbb{F}}_4$. Here $P(x) = x^2 + x + 1$ is the primitive
polynomial of ${\mathbb{F}}_4$ and $P(\alpha) = 0$. 
\begin{figure}[htb]
\centerline{
\includegraphics[scale=0.4]{2bitmult.eps}
}
\caption{\small A 2-bit Multiplier over ${\mathbb{F}}_{2^2}$. The gate
  $\otimes$ corresponds to AND-gate, i.e. bit-level multiplication
  modulo 2. The gate $\oplus$ corresponds to XOR-gate, i.e. addition
  modulo 2.} 
\label{fig:mul2bit}
\end{figure}

The functionality of the entire circuit can be described using the
following polynomials derived from the Boolean gate-level operators: 
$f_1: z_0+z_1\alpha +Z; ~~f_2: b_0+b_1\alpha +B; ~~f_3: a_0+a_1 \alpha
+A; ~~f_4: s_0+a_0 \cdot b_0; ~~f_5: s_1+a_0 \cdot b_1; ~~f_6:
s_2+a_1 \cdot b_0; ~~f_7: s_3+a_1 \cdot b_1; ~~f_8: r_0+s_1 + s_2;
~~f_9: z_0+s_0 + s_3; ~~f_{10}: z_1 + r_0 + s_3$. If we impose the
following {\bf elimination} term order: {\bf lex term order} with
``circuit variables'' $>$ ``Output Z'' $>$ ``Inputs, A, B''
%More precisely, we can use {\bf lex} term order with $s_0 > s_1 >  s_2 >
%s_3 >  r_0 > a_0 > a_1 > b_0 > b_1 > g_0 > g_1 > A > B > G$.
%The above term order is an {\bf elimination} order. If we use the above
and compute a Gr\"obner basis $G$ of $\{f_1, \dots, f_{10}\}$, we observe
the following polynomials in the basis:  $g_1: z_0+z_1\alpha +Z;
~~g_2: b_0+b_1\alpha +B; ~~g_3: a_0+a_1 \alpha +A; ~~g_4: s_3+r_0+z_1;
g_5: s_1+s_2+r_0; ~~g_6: s_0+s_3+z_0; ~~{\mathbf{g_7: Z +  AB}}; ~~g_8:
a_1b_1+a_1B+b_1A+z_1; ~~g_9: r_0+a_1b_1+z_1; ~~g_{10}:
s_2+a_1b_0$. Notice that the polynomial $g_7: Z + AB$ describes $Z =
AB$ as the (canonical) polynomial function implemented by the circuit;
and we were able to {\it extract} this representation using the
Gr\"obner basis computation. We wish to explore such an approach to
derive an efficient decision procedure for word-level abstraction. 
}
\end{Example}

%\subsection{Contributions of this Thesis}
{\bf Contributions of this Thesis:} Our approach to solve this
problem, and the contributions of this thesis, can be outlined as
follows:

@@

\item Based on the concepts of {\it Strong Nullstellensatz, Gr\"obner
  bases, elimination ideals and projections of varieties}
  \cite{ideals:book}, we deduce that the polynomial abstraction
  problem can be formulated as one of {\it computing a Gr\"obner
    basis} of the set of polynomials derived from the given circuit
  netlist, using a specific elimination term order $>$.

\item Computing Gr\"obner bases using elimination term orders is
  infeasible for large circuits. To overcome this limitation, we will
  investigate the use of the FGLM algorithm \cite{fglm} to derive the
  polynomial representation. The FGLM algorithm takes an {\it already
    computed} Gr\"obner basis ($G_1$) w.r.t. an arbitrary term order
  $>_1$, and transforms it into another Gr\"obner basis ($G$)
  w.r.t. an elimination term order $>$. In the PhD thesis of {\it
  Lv} \cite{lv:phd}, it was shown that for any given
  circuit, there exists a term order $>_1$ that renders the set of
  polynomials derived from the circuit itself a Gr\"obner
  basis. Moreover, $>_1$ can be easily derived by performing a reverse
  topological traversal of the circuit. Consequently, $G_1$ is readily
  available as a Gr\"obner basis directly by construction. Using FGLM,
  we can then translate $G_1$ into the Gr\"obner basis $G$
  w.r.t. the required elimination order $>$.

\item The worst-case complexity of computing a Gr\"obner basis is
  known to be doubly exponential in $n$, the number of variables, and
  polynomial in $d$, the degree of the ideal. Most hardware/software
  verification applications do exhibit such high complexity, as the
  number of intermediate computations in the Buchbeger's algorithm
  \cite{buchberger_thesis} 
  tend to explode. Therefore, we conjecture that using the FGLM
  algorithm --- which relies on sparse linear algebra concepts ---
  perhaps this complexity can be avoided. In this thesis, we will
  develop a CAD framework using the above ideas and investigate the
  scalability of our methods.

\item As an application, we will use our CAD approach to
  reverse-engineer the function implemented by a given Galois field
  arithmetic circuits used in ECC   implementations. This can be used
  for function identification from a given circuit for formal
  verification.

@@

{\bf Proposal Organization:} The next section reviews previous work in
the area of canonical representations functions, word-level
abstractions, formal design verification using computer algebra
techniques, and also polynomial interpolation literature in symbolic
computing. Section \ref{sec:prelimgf} reviews 
Galois field theory and hardware design. Section \ref{sec:ideals}
reviews preliminary computer-algebra concepts related to ideals,
varieties, Gr\"obner bases, elimination ideals and
Nullstellensatz. Section \ref{sec:theory} describes our results on
polynomial abstraction from circuits, and demonstrates the application
of our work using preliminary experiments. The application of the FGLM
algorithm is covered in Section \ref{sec:fglm}. Finally, Section
\ref{sec:obj} outlines the research plan and concludes the proposal.

>>>>

Abstraction of word-level functionality from bit-level descriptions of
digital circuits is an important fundamental problem in Electronic
Design Automation (EDA) and design verification. Word-level abstractions
find applications in high-level/RTL datapath synthesis
%\cite{demicheli:iccad_98} \cite{demicheli:dac_99}
\cite{demicheli:tcad_03}, RTL verification \cite{WLS} %\cite{arditi:bmd}
\cite{lpsat}, word-level SMT and constraint solving \cite{ms:research}
\cite{boolector}, %\cite{tew:iccad08}, 
etc. Functional abstraction can
also be helpful in detecting malicious modifications to a circuit --
potentially inserted as hardware Trojan horses -- by
{\it reverse-engineering} the function implemented by the circuit\footnote{A
hardware Trojan modifies the functionality of the 
circuit. Abstraction of the function at word-level can perhaps give
some insights into the functional {\it intent} of the Trojan. This can
also be helpful in Trojan classification; such efforts are
currently underway within the EDA community \cite{Bhunia:Trojan}.}. 
It is further desirable that the obtained word-level abstraction be a
{\it canonical} representation of the function, to facilitate
equivalence verification between a specification model and an
implementation circuit.

This paper presents a symbolic method to derive the {\it word-level,
  canonical, polynomial representation} from a given combinational
circuit. Our approach models the problem over Galois fields, and employs
concepts from commutative algebra and algebraic geometry ---
notably, Gr\"obner bases \cite{ideals:book} theory and
technology --- to derive the word-level abstraction.
%Buchberger's algorithm
%\cite{buchberger_thesis}, elimination ideals 
%and the FGLM algorithm \cite{fglm}.

The main motivation for this work is to ``reverse engineer'' (or
to identify) the function implemented by a given Galois field
arithmetic circuit as used in Elliptic Curve Cryptography (ECC). The
main operations of encryption, decryption and authentication in ECC
rely on point-addition and point-doubling operations on elliptic
curves defined over Galois fields $\Fkk$. These primitive operations
are, in turn, implemented as circuits that perform polynomial
computations over $k$-bit vectors \cite{eccld}. 
%Moreover, the datapath size $k$ in these applications
%can be very large, {\it e.g.} $k = 163, 233$ and larger, as specified
%by the US National Institute for Standards and Technology (NIST) for
%ECC. 
The objective is to apply our approach to a given circuit and
{\it extract  the word-level polynomial function (polyfunction)}
implemented by it for design verification. While our approach can be
applied to any arbitrary combinational circuit, it is most beneficial
for arithmetic circuits where canonical Boolean representations prove
to be infeasible.

{\bf Problem Statement:} Given a combinational circuit $C$ with
$k$-bit inputs and $k$-bit outputs, such that the circuit implements 
Boolean functions that are mappings between $k$-dimensional Boolean
spaces: $f: \B^k \rightarrow \B^k$. Let $\{a_0, \dots, a_{k-1}\}$
denote the primary inputs of the circuit, and let $\{y_0, \dots,
y_{k-1}\}$ denote the bit-level primary outputs. Suppose that we do
not know the function implemented by the circuit. We wish to
derive a {\it word-level, symbolic representation} of the function as
$Y = \F(A)$ over $\Fkk$, where $Y = \{y_0, \dots, y_{k-1}\}$, $A =
\{a_0, \dots,  a_{k-1}\}$ are, respectively, the output and input
bit-vectors (words), and $\F$ denotes a polynomial representation of
the function $f$. We wish to further generalize our approach to any
circuit with arbitrary number  of inputs ($n$) and outputs ($m$), as
polyfunctions $f: {\mathbb{F}}_{2^n} \rightarrow
{\mathbb{F}}_{2^m}$.

{\bf Approach:} Canonical symbolic DAG 
representations of Boolean functions, such
as ROBDDs \cite{BRYA86}, FDDs \cite{okfdd}, BMDs \cite{bmd}, etc., are
based on (variants of) the Shannon's  expansion, which is a bit-wise,
Boolean decomposition. These are inapplicable to 
word-level abstraction of modulo-arithmetic circuits over Galois
extension fields $\Fkk$. Therefore, we approach this problem from the
perspective of {\it symbolic computer algebra and algebraic geometry}.

@@

First of all, {\it not every
  function} of the type $f: \Z_{2^k} \rightarrow \Z_{2^k}$, is a
polynomial function; i.e. every function cannot be represented by a
polynomial $\F \pmod{ 2^k}$.  In commutative algebra, identification of
such polynomial functions is an important problem: given a function
$f: \Z_n \rightarrow \Z_n$, $n \in {\mathbb{N}}$, identify if $f$ has
a polynomial representation. If so, derive a unique,
minimal, canonical polynomial $\F$, such that $f \equiv  \F \pmod{
  n}$. 
%that represents $f$. 
%This
%requires to analyze $f$ at each of the $n$ points, and to setup a
%system of $n$ linear congruences to solve. If this system of
%congruences has a solution, then $f$ is a polynomial function; 
%otherwise, $f$ is not a polynomial function. And the feasible
%solutions to these linear congruences correspond to the coefficients
%of a polynomial $\F$ that represents $f$.  
The work of 
\cite{singmaster} 
%\cite{chen_95} \cite{chen_96} 
addresses such problems in number theory and algebra. {\it
 Shekhar et al.} \cite{shekhar:tcad07} address RTL verification
of polynomial datapaths over $k$-bit vectors using the above
concepts. However, in their work, the RTL datapath is already known to
be a polynomial function $\pmod{ 2^k}$. Unfortunately, an arbitrary
$k$-input/$k$-output combinational circuit cannot always be modeled as
a polynomial function over $\Z_{2^k}$; therefore, the $\Z_{2^k}$ model
is not considered in this work.

On the other hand, there is a well-known ``textbook'' result
\cite{ff:1997} which states that over Galois fields ($\Fq$) of $q$
elements, {\it every function} $f: \Fq \rightarrow \Fq$ is a
polynomial function. 
%By analyzing $f$ over each of the $q$ points, one can apply
%Langrange's interpolation formula and interpolate a polynomial $\F(x)
%= \sum_{k=1} ^q  \frac{ \prod_{i \neq k}  (x -x_i)}{\prod_{i \neq k}
%  (x_k -x_i)} \cdot f(x_k)$, which is a polynomial of degree at 
%most $q-1$ in $x$. One can easily see that $\F(a)=f(a)$ for all $a \in
%\Fq$, and $\F(x)$ is therefore the polynomial function representation
%of $f$. 
Motivated by this fundamental result, we devise an approach
to derive a word-level polynomial function abstraction from the
circuit using the $f: \Fkk \rightarrow \Fkk$ polyfunction model. 
%Given the circuit $C$ which represents a function $f:
%\B^k \rightarrow \B^k$, we interpret $f$ as a function $f: \Fkk
%\rightarrow \Fkk$, and derive a unique, minimal, canonical polynomial
%representation as $Y = \F(A)$ over $\Fkk$, where $Y, A$ are,
%respectively, the output and input bit-vectors of the circuit
%$C$. 
%Note, however, that we are not given a function (mapping);
%rather, we are given a circuit, which is an encoding of the
%function. Interpolating a polynomial $\F$ over $2^k$ points is
%also going to be infeasible for large values of $k$. Therefore, 
We analyze the circuit, derive a specific set of polynomials modeled
over $\Fkk$, and compute a {\it Gr\"obner basis} of these polynomials
with a specific term order to abstract the canonical polynomial
representation. Our approach can be generalized to a circuit with
arbitrary number of inputs and outputs, i.e. to model polynomial
functions $f: \Fkk^d \rightarrow \Fkk$, and further to $f:
{\mathbb{F}}_{2^n} \rightarrow {\mathbb{F}}_{2^m}$.

%\subsection{Contributions of this Thesis}
{\bf Approach \& Contributions:}

@@

\item Based on the concepts of {\it Strong Nullstellensatz, Gr\"obner
  bases, elimination ideals and projections of varieties}
  \cite{ideals:book}, we deduce that the polynomial abstraction
  problem can be formulated as one of {\it computing a Gr\"obner
    basis} of a set of polynomials derived from the given circuit
  netlist, using a specific elimination term order $>$.

\item Computing Gr\"obner bases using elimination term orders is
  infeasible for large circuits. To overcome this limitation, we 
  investigate the use of the FGLM algorithm \cite{fglm} to derive the
  polynomial representation. The FGLM algorithm takes an {\it already
    computed} Gr\"obner basis ($G_1$) w.r.t. an arbitrary term order
  $>_1$, and transforms it into another Gr\"obner basis ($G$)
  w.r.t. an elimination term order $>$. In the work of {\it
  Lv} \cite{lv:date2012} it was shown that for any
  given circuit, there exists a term order $>_1$ that renders the set
  of polynomials derived from the circuit itself a Gr\"obner
  basis. Moreover, $>_1$ can be easily derived by performing a reverse
  topological traversal of the circuit. Consequently, $G_1$ is readily
  available as a Gr\"obner basis directly by construction. Using FGLM,
  we can then translate $G_1$ into the Gr\"obner basis $G$
  w.r.t. the required elimination order $>$.

\item The worst-case complexity of computing a Gr\"obner basis is
  known to be doubly exponential in $n$, the number of variables, and
  polynomial in $d$, the degree of the ideal. Most hardware/software
  verification applications do exhibit such high complexity, as the
  number of intermediate computations in the Gr\"obner basis algorithm
  (Buchbeger's algorithm) \cite{buchberger_thesis} 
  tend to explode. Therefore, we conjecture that using the FGLM
  algorithm --- which relies on {\it sparse linear algebra concepts}
  --- perhaps this complexity can be avoided. We are currently
  implementing a domain specific FGLM algorithm --- specifically for
  the abstraction problems related to Galois field
  crypto-circuits. Experimental results with FGLM are not yet available.

%\item As an application, we will use our CAD approach to
%  reverse-engineer the function implemented by a given Galois field
%  arithmetic circuits used in ECC   implementations. This can be used
%  for function identification from a given circuit for formal
%  verification.

@@

{\bf Paper Organization:} The next section reviews previous work in
the area of canonical representations functions, word-level
abstractions, 
%formal design verification using computer algebra techniques, 
and also polynomial interpolation literature in symbolic
computing. Section \ref{sec:prelimgf} reviews 
Galois field theory and describes the arithmetic circuits that we wish
to verify using our approach. Section \ref{sec:ideals}
reviews preliminary computer-algebra concepts related to ideals,
varieties, Gr\"obner bases, elimination ideals and
Nullstellensatz. Section \ref{sec:theory} describes our results on
polynomial abstraction from circuits, and demonstrates the application
of our work using preliminary experiments. The application of the FGLM
algorithm is covered in Section \ref{sec:fglm}. Finally, Section
\ref{sec:concl} concludes the proposal.

### 2014-04-25 sequential/latex/abstraction/iwls/xiaojun.tex
upload files from laptop linux

Bit level circuit variables including primary inputs/outputs can only take value
within $\Z_2$. They can also be written in functions of other variables and constants.
In computer algebra, circuit variable $a$ can be described as a polynomial, that is
$a = f(x_0, x_1, \dots, x_{n-1}) \in {\mathbb{F}}[x]$. Moreover, circuit variable can
have multiple specifications, they can be written in polynomials and included in an
ideal $I = \{f_0, f_1, \dots, f_k\}$. The varieties of this ideal are possible 
assignments of circuit variables. Similarly for $n$ bits world-level circuit 
variables, the varieties are elements from $\Fkk$. Thus it's convenient to use
ideals and varieties to describle circuit variables. \\

\begin{Definition}
({\bf Sum of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then the 
{\bf sum} of $I$ and $J$, denoted by $I + J$, is the set
  \begin{equation}
  I + J = \{f + g : f \in I \ and\  g \in J\}.
  \end{equation}
Furthermore, if $I = \langle f_1, \dots, f_r\rangle$ and 
$J = \langle g_1, \dots, g_s\rangle$, then 
$I + J = \langle f_1, \dots, f_r, g_1, \dots, g_s\rangle$.
\end{Definition}

\begin{Definition}
({\bf Product of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then the
{\bf product} of $I$ and $J$, denoted by $I \cdot J$, is defined to be the ideal generated 
by all polynomials $f \cdot g$ where $f \in I$ and $g \in J$. Furthermore, let
$I = \langle f_1, \dots, f_r\rangle$ and $J = \langle g_1, \dots, g_s\rangle$, then
  \begin{equation}
  I \cdot J = \langle f_ig_j : 1 \leq i \leq r, 1 \leq j \leq s\rangle .
  \end{equation}
\end{Definition}

\begin{Definition}
({\bf Quotient of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then $I:J$
is the set
  \begin{equation}
  \{f \in k[x_1, \dots, x_n] : fg \in I, \forall g \in J\}
  \end{equation}
and is called the {\bf ideal quotient} of $I$ by $J$.
\end{Definition}

According to definitions above, it is possible to calculate ideal sum, product and 
quotient based on ideal generators. Additional conclusion about union, 
intersection and complement of varieties can be attained below: \\

\begin{Theorem}
\label{thm:unionintersect}
If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then ${\bf V}(I + J) = {\bf V}(I)
\bigcap {\bf V}(J)$ and ${\bf V}(I \cdot J) = {\bf V}(I) \bigcup {\bf V}(J)$.
\end{Theorem}

\begin{Theorem}
\label{thm:quotient}
Let $V$ and $W$ be varieties in $\Fkk$. Then ${\bf I}(V) : {\bf I}(W) = 
{\bf I}(V - W)$.
\end{Theorem}

For \ref{thm:quotient}, let $V = \Fkk = {\bf V}(\langle vanishing \  polynomials
\rangle)$, then $V - W$ is the \textbf{complementary set} of variety $W$.\\

@@

\section{Sequential circuits and Finite State Machine}
\label{sec:fsm}
\subsection{Introduction to Finite State Machine:}
Borrow from somewhere.
\subsection{Symbolic Image Computation:}
Borrow from somewhere.
\subsection{Implicit State Enumeration:}
BFS algorithm below:
\begin{algorithm}[hbt]
\SetAlgoNoLine
 \KwIn{Transition functions $\Delta$, initial state $S^0$}

  $from^0 = reached = S^0$\;
  \Repeat{$new^i == 0$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$Img$(\Delta, from^{i-1})$\;
	$new^i \gets to^i \cdot \overline{reached}$\;
  	$reached \gets reached + new^i$\;
	$from^i \gets new^i$\;
  }
\Return{$reached$}
\caption {Breadth-first Traversal Algorithm}\label{alg:gb}
\end{algorithm}

@@

The following mapping from Boolean operations to Galois field $\mathbb{F}_2$ 
operations is straightforward. Assuming $a$ and $b$ are both bit-level variables:
\begin{itemize}
  \item $\overline{a} \rightarrow 1 + a$
  \item $a\ and\ b \rightarrow ab$
  \item $a\ or\ b \rightarrow a + b + ab$
\end{itemize}
Comparing to the quantification approach in \ref{sec:fsm}, using Gr\"obner bases
approach from \ref{sec:theory}. Construct an elimination ideal with following 
polynomials: $f_1: 1 + XNOR(t_0, OR(p\cdot q, (1 + x_i)\cdot(1 + p)\cdot(1 + q))); 
f_2: 1 + XNOR(t1, OR(xi\cdot(1+p),p\cdot(1+q))); f_3: S - p - q\cdot\alpha; 
f_4: T - t_0 - t_1\cdot \alpha$ and vanishing polynomials $f_5: p^2 - p; 
f_6: q^2 - q; f_7: t_0^2 - t_0; f_8: t_1^2 - t_1; f_9: S^4 - S; f_{10}: x_i^2 - x_i; 
f_{11}: T^4 - T$, where $S$ and $T$ are 2-bit word representing current state
and next state as defined in $f_3$ and $f_4$, $f_1$ and $f_2$ describe the 
transition relations. At last the initial state should also be included in 
this elimination ideal. For example initial state is $S_3$, then last polynomial
is $f_{12}: S + 1 + \alpha$. According to elimination theorem \ref{thm:elim},
let the lex ordering be $\{all\ others\} > T$, calculate Gr\"obner basis, the 
result must contain a polynomial with only one variable $T$, which can indicate
the possible assignments of next state. \par

>>>>

Bit level circuit variables including primary inputs/outputs can only take value
within $\Z_2$. They can also be written in functions of other variables and constants.
In computer algebra, circuit variable $a$ can be described as a polynomial, that is
$a = f(x_0, x_1, \dots, x_{n-1}) \in {\mathbb{F}}[x]$. Moreover, circuit variable can
have multiple specifications, they can be written in polynomials and included in an
ideal $I = \{f_0, f_1, \dots, f_k\}$. The varieties of this ideal are possible 
assignments of circuit variable. Similarly for $n$ bits world-level circuit 
variables, the varieties are elements from $\Fkk$. Thus it's convenient to use
ideals and varieties to describle circuit variables. \par

\begin{Definition}
({\bf Sum of Ideals}) If I and J are ideals in $k[x_1, \dots, x_n]$, then the 
{\bf sum} of I and J, denoted I + J, is the set
  \begin{equation}
  I + J = \{f + g : f \in I and g \in J\}.
  \end{equation}
Furthermore, if $I = \langle f_1, \dots, f_r\rangle$ and 
$J = \langle g_1, \dots, g_s\rangle$, then 
$I + J = \langle f_1, \dots, f_r, g_1, \dots, g_s\rangle$.
\end{Definition}

\begin{Definition}
({\bf Product of Ideals}) If I and J are ideals in $k[x_1, \dots, x_n]$, then the
{\bf product} of I and J, denoted $I \cdot J$, is defined to be the ideal generated 
by all polynomials $f \cdot g$ where $f \in I$ and $g \in J$. Furthermore, let
$I = \langle f_1, \dots, f_r\rangle$ and $J = \langle g_1, \dots, g_s\rangle$, then
  \begin{equation}
  I \cdot J = \langle f_ig_j : 1 \leq i \leq r, 1 \leq j \leq s\rangle .
  \end{equation}
\end{Definition}

\begin{Definition}
({\bf Quotient of Ideals}) If I and J are ideals in $k[x_1, \dots, x_n]$, then I:J
is the set
  \begin{equation}
  \{f \in k[x_1, \dots, x_n] : fg \in I \forall g \in J\}
  \end{equation}
and is called the {\bf ideal quotient} of I by J.
\end{Definition}

According to definitions above, it's possible to calculate ideal sum, product and 
quotient based on ideal generators. Additionally conclusion about union, 
intersection and complement of varieties can be attained below: \par

\begin{Theorem}
\label{thm:unionintersect}
If I and J are ideals in $k[x_1, \dots, x_n]$, then ${\bf V}(I + J) = {\bf V}(I)
\bigcap {\bf V}(J)$ and ${\bf V}(I \cdot J) = {\bf V}(I) \bigcup {\bf V}(J)$.
\end{Theorem}

\begin{Theorem}
\label{thm:quotient}
Let V and W be varieties in $\Fkk$. Then ${\bf I}(V) : {\bf I}(W) = 
{\bf I}(V - W)$.
\end{Theorem}

For \ref{thm:quotient}, let $V = \Fkk = {\bf V}(\langle vanishing polynomials
\rangle)$, then $V - W$ is the complementary set of variety $W$.\\

@@

\section{Sequential circuits and Finite State Machine}
\label{sec:fsm}
{\bf Introduction to Finite State Machine:}\par
{\bf Symbolic Image Computation:}\par
{\bf Implicit State Enumeration:}\par

@@

The following mapping from Boolean operations to Gal\"ois field $\mathbb{F}_2$ 
operations is straightforward. Assuming $a$ and $b$ are both bit-level variables:
\begin{itemize}
  \item $\bar{a} \rightarrow 1 + a$
  \item $a and b \rightarrow ab$
  \item $a or b \rightarrow a + b + ab$
\end{itemize}
Comparing to the quantification approach in \ref{sec:fsm}, using Gr\"obner bases
approach from \ref{sec:theory}. Construct an elimination ideal with following 
polynomials: $f_1: 1 + XNOR(t0, OR(p\cdot q, (1+xi)\cdot(1+p)\cdot(1+q))); 
f_2: 1 + XNOR(t1, OR(xi\cdot(1+p),p\cdot(1+q))); f_3: S - p - q\cdot\alpha; 
f_4: T - t0 - t1\cdot\alpha$ and vanishing polynomials $f_5: p^2 - p; 
f_6: q^2 - q; f_7: t0^2 - t0; f_8: t1^2 - t1; f_9: S^4 - S; f_{10}: xi^2 - xi; 
f_{11}: T^4 - T$, where $S$ and $T$ are 2-bit word representing current state
and next state as defined in $f_3$ and $f_4$, $f_1$ and $f_2$ describe the 
transition relations. At last the initial state should also be included in 
this elimination ideal. For example initial state is $S_3$, then last polynomial
is $f_{12}: S + 1 + \alpha$. According to elimination theorem \ref{thm:elim},
let the lex ordering be $\{all others\} > T$, calculate Gr\"obner basis, the 
result must contain a polynomial with only one variable $T$, which can indicate
the possible assignments of next state. \par
